---
title: "Mapping the Politics of the New Global South, Progress Update"
author: "Neeraj Sharma"
date: "7/31/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r echo = FALSE}
# Relevant to data importation, structuring and visualization
library(tidyverse)
library(knitr)
library(readr)
library(here)

# Relevant to data formatting
library(lubridate)
library(countrycode)

# Relevant to text analysis
library(tidytext)
library(stringr)
library(SnowballC)
library(textclean)

# Used for webscraping
library(rvest)
```

```{r echo = FALSE}
unigrams_corpus_1970on <- read_tsv(here::here("Data", "unigrams_mikhaylov_project.tsv")) %>%
  select(Session, Year, Country, word, word_stem) %>%
  drop_na() %>%
  # Manually add some stemming for important words and terms that didn't get all variants stemmed
  mutate(word_stem = if_else(word == "african", "africa", word_stem)) %>%
  mutate(word_stem = if_else(word == "environmental", "environ", word_stem))
  

bigrams_corpus_1970on <- read_tsv(here::here("Data", "bigrams_mikhaylov_project.tsv")) %>%
  select(Session, Year, Country, first_word_stem, second_word_stem, word_stem)
```

---
# Introduction

I am working for Professor Mark Bradley in the History Department at the University of Chicago this summer on his research project, Mapping the Politics of the New Global South. 


## Import datasets

These datasets were produced through the corpus_maker.R script. The original source files are from Mikhaylov.


## Glimpse at the content of the datasets

Unigrams

```{r}
kable(unigrams_corpus_1970on %>% slice(1:10))
```

Bigrams

```{r}
kable(bigrams_corpus_1970on %>% filter(Session == 25) %>% slice(1:10))
```
---

# Stop Words

This is a list of stemmed words that appear so much in the dataset that they are essentially noise. This is a list object that is called later on to remove these so-called "stop words." I have listed them out here so the reader is aware what UN-specific words have been cleaned out of the data. I reference data about country references in my notes, but they will not appear in these graphs. 

```{r}
UN_stop_words <- tibble(words = c("nation", 
                                  "unit", 
                                  "intern", 
                                  "countri", 
                                  "develop", 
                                  "peac",
                                  "world",
                                  "peopl",
                                  "deleg",
                                  # Stops countries from counting their own names as very commonly repeated words. Stripping removes casing. This takes codelist from countrycode. It might be bad because it eliminates when speeches mention other countries. 
                                  strip(codelist$country.name.en)
                                  ))
```

# Looking at specific countries common words over time

I was encouraged by Professor Bradley to investigate keyword trends over time in the following countries:

* Indonesia
* Algeria
* Kenya
* Mexico
* Egypt

What I've done is to group the speeches of each country into 5 year increments and then took the top 10 words identified in each chunk. This allows us to see what keywords rise and fall over time. Here is what emerged based on this analysis.

## Indonesia

```{r fig.height = 8, fig.width = 10, echo = FALSE}
indonesia_count_word_year <- unigrams_corpus_1970on %>%
  filter(Country == "Indonesia") %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  mutate(Year = cut_interval(Year, length = 5)) %>%
  group_by(Year) %>%
  count(word_stem) %>%
  group_by(Year) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(Year = as.factor(Year),
           name = reorder_within(word_stem, n, Year))

ggplot(data = indonesia_count_word_year, mapping = aes(x = name, y = percent, fill = Year)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~Year, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Count (Percent of All Relevant Words Said During Period)",
         x = NULL,
         title = "Most Common Words Over Time (Indonesia)") +
    theme(title = element_text(size = 14), strip.text.x = element_text(face = "bold"), axis.text.y = element_text(size = 12))
```

Interesting observations:

* The word "Partnership" arises in the range of 2006-2010. This is interesting because it's right at the start of the rise of the usage of the term "Global South" per my understanding, which is importent as it indicates a shift towards a cooperative outlook towards foreign policy potentially.
* ASEAN becoming a continually present term starting in 2000.
* Words like "commit," "goal," etc. appear more in the later years. Generally, the tone is more outward looking and cooperative. 

## Algeria

```{r fig.height = 8, fig.width = 10, echo = FALSE}
algeria_count_word_year <- unigrams_corpus_1970on %>%
  filter(Country == "Algeria") %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  mutate(Year = cut_interval(Year, length = 5)) %>%
  group_by(Year) %>%
  count(word_stem) %>%
  group_by(Year) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(Year = as.factor(Year),
           name = reorder_within(word_stem, n, Year))

ggplot(data = algeria_count_word_year, mapping = aes(x = name, y = percent, fill = Year)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~Year, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Count (Percent of All Relevant Words Said During Period)",
         x = NULL,
         title = "Most Common Words Over Time (Algeria)") +
    theme(title = element_text(size = 14), strip.text.x = element_text(face = "bold"), axis.text.y = element_text(size = 12))
```

Interesting observations:

* Terrorism is a key phrase mentioned a lot during the later period of the civil war. 
* Crisis is said a lot in 1980s. Not exactly sure why that's the case. I don't know much about Algeria but my quick internet investigation couldn't reveal anything obvious. 
* Any changes from 1970 to 2018 not as apparent as other countries. It's not the most revealing country to see changes in the discourse surrounding development. 

## Kenya

```{r fig.height = 8, fig.width = 10, echo = FALSE}
kenya_count_word_year <- unigrams_corpus_1970on %>%
  filter(Country == "Kenya") %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  mutate(Year = cut_interval(Year, length = 5)) %>%
  group_by(Year) %>%
  count(word_stem) %>%
  group_by(Year) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(Year = as.factor(Year),
           name = reorder_within(word_stem, n, Year))

ggplot(data = kenya_count_word_year, mapping = aes(x = name, y = percent, fill = Year)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~Year, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Count (Percent of All Relevant Words Said During Period)",
         x = NULL,
         title = "Most Common Words Over Time (Kenya)") +
    theme(title = element_text(size = 14), strip.text.x = element_text(face = "bold"), axis.text.y = element_text(size = 12))
```

Interesting observations:

* Cooperate and global appear as keywords in 1990-1995. 
* Language of cooperation definately has changed in the early period compared to the late period. 
* Relations with Somalia seem to be very important in the late 2000s. They seem to have started campaigns against Al-Shabab around that time.
* This trend appears to continue through the rest of the 2000s with mentions of Sudan, Somalia again, Support, and Sustain.

## Mexico

```{r fig.height = 8, fig.width = 10, echo = FALSE}
mexico_count_word_year <- unigrams_corpus_1970on %>%
  filter(Country == "Mexico") %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  mutate(Year = cut_interval(Year, length = 5)) %>%
  group_by(Year) %>%
  count(word_stem) %>%
  group_by(Year) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(Year = as.factor(Year),
           name = reorder_within(word_stem, n, Year))

ggplot(data = mexico_count_word_year, mapping = aes(x = name, y = percent, fill = Year)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~Year, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Count (Percent of All Relevant Words Said During Period)",
         x = NULL,
         title = "Most Common Words Over Time (Mexico)") +
    theme(title = element_text(size = 14), strip.text.x = element_text(face = "bold"), axis.text.y = element_text(size = 12))
```

Interesting observations:

* Human rights are a big deal in 200s onward period recently. Especially in 2015, they are at the forefront of topics discussed. 
* Drug crime and climate change are themes in 2000s
* Nuclear weapons and international security appear to be concerns for Mexico? The terms appear frequently in multiple different decades which indicates a continuing interest in this topic. It obviously makes sense given that nuclear technology is always a concern for nations, but it seems interesting for a country that has renounced the ability to make weapons (Treaty of Tlatelolco, 1968).

## Egypt

```{r fig.height = 8, fig.width = 10, echo = FALSE}
egypt_count_word_year <- unigrams_corpus_1970on %>%
  filter(Country == "Egypt") %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  mutate(Year = cut_interval(Year, length = 5)) %>%
  group_by(Year) %>%
  count(word_stem) %>%
  group_by(Year) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(Year = as.factor(Year),
           name = reorder_within(word_stem, n, Year))

ggplot(data = egypt_count_word_year, mapping = aes(x = name, y = percent, fill = Year)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~Year, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Count (Percent of All Relevant Words Said During Period)",
         x = NULL,
         title = "Most Common Words Over Time (Egypt)") +
    theme(title = element_text(size = 14), strip.text.x = element_text(face = "bold"), axis.text.y = element_text(size = 12))
```

Interesting observations:

* Egypt talks about Palestine a lot, especially in the early periods of this analysis. That is not surprising AT ALL.
* While some countries focus on economy in their speeches, Egypt has not made it a focus of their speeches. Rather, their concern seems much more rooted in the geopolitics of North Africa. They mention the Arab World, Palestine, and Africa and words related to policy in these areas much more than words like global or economy. 

# Common Words by Decade

```{r}
words_decades <- unigrams_corpus_1970on %>%
  mutate(decade = paste0(substr(Year, 1, 3), "0s", sep = "")) %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  group_by(decade) %>%
  count(word_stem) %>%
  group_by(decade) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(decade = as.factor(decade),
           name = reorder_within(word_stem, n, decade))
```

```{r}
ggplot(data = words_decades, mapping = aes(x = name, y = n, label = n)) +
  geom_col() +
  geom_text(hjust = 1.1, size = 3, fontface = "bold", color = "White") +
  coord_flip() +
  scale_x_reordered() +
  scale_y_continuous(expand = c(0,0)) +
  facet_wrap(~ decade, scales = "free_y") +
  labs(title = "Most common words over time (all nations)", x = "Words (Stemmed)", y = "Number of Mentions")
```

Old example I have written that works well to provide an alternative way of graphing words over time. This is being kept here just for example's sake and isn't doesn't have good underlying data.

```{r}
seventies_freq <- unigrams_corpus_1970on %>%
  filter(Year == 1970 ) %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  group_by(word_stem) %>%
  count(sort = TRUE) %>%
  arrange(desc(n)) %>%
  ungroup() %>%
  mutate(percent = n/sum(n))


ggplot(data = seventies_freq %>% slice(1:10), mapping = aes(x = reorder(word_stem, n), y = n, label = n)) +
  geom_col() +
  geom_text(hjust = 1.5, fontface = "bold", color = "White") +
  coord_flip() +
  labs(title = "Most common words in 1970", x = "Words (Stemmed)", y = "Number of Mentions")
```

# Common words using 1989 as the dividing point

```{r}
words_divided <- unigrams_corpus_1970on %>%
  mutate(Era = if_else(Year <= 1989, "1 Before or Equal to 1989", "2 After 1989")) %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  group_by(Era) %>%
  count(word_stem) %>%
  group_by(Era) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(Era = as.factor(Era),
           name = reorder_within(word_stem, n, Era))
```

```{r}
ggplot(data = words_divided, mapping = aes(x = name, y = n, label = n)) +
  geom_col() +
  geom_text(hjust = 1.1, size = 3, fontface = "bold", color = "White") +
  coord_flip() +
  scale_x_reordered() +
  scale_y_continuous(expand = c(0,0)) +
  facet_wrap(~ Era, scales = "free_y") +
  labs(title = "Most common words over time (Split by Era)", x = "Words (Stemmed)", y = "Number of Mentions")
```

# Looking at specific words overtime globally

```{r}
overtime <- unigrams_corpus_1970on %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  filter(word_stem == "environ" | word_stem == "climat" | word_stem == "resili" | word_stem == "sustain" | word_stem == "capabl") %>%
  # hybriditiy never mentioned
  group_by(Year, word_stem) %>%
  count()

others_overtime <- overtime %>%
  filter(word_stem == "resili"  | word_stem == "capabl")

cc_overtime <- overtime %>%
  filter(word_stem == "climat" | word_stem == "environ")

ggplot(data = overtime, mapping = aes(x = Year, y = n, color = word_stem)) +
  geom_path() +
  labs(title = "Count of focus words over time", y = "Number of Mentions", color = "Word Stem")

ggplot(data = others_overtime, mapping = aes(x = Year, y = n, color = word_stem)) +
  geom_path() +
  labs(title = "Mentions of words related to capacity over time", y = "Number of Mentions", color = "Word Stem")

ggplot(data = cc_overtime, mapping = aes(x = Year, y = n, color = word_stem)) +
  geom_path() +
  labs(title = "Mentions of words related to climate over time", y = "Number of Mentions", color = "Word Stem")

```

# Scraping table for Global North/South orientation

```{r}
northsouth <- read_html("https://meta.wikimedia.org/wiki/List_of_countries_by_regional_classification")
nonaligned <- read_html("https://www.worlddata.info/alliances/non-aligned-movement.php")
```

```{r fig.height = 8, fig.width = 10, echo = FALSE}
northsouth_tbl <- html_nodes(northsouth, css = "table") %>%
  # get the first table
  nth(1) %>%
  # convert to data frame
  html_table(header = TRUE) %>%
  # Override Singapore classification to make it part of global south
  mutate(`Global South`, `Global South` = if_else(`Country` == "Singapore", "Global South", `Global South`)) %>%
  mutate(`Global South`, `Global South` = as.factor(`Global South`)) %>%
  mutate(Region = countrycode(Country, origin = "country.name", destination = "region")) %>%
  drop_na()

nonaligned_tbl <- html_nodes(nonaligned, css = "table") %>%
  # get the first table
  nth(1) %>%
  # convert to data frame
  html_table(header = TRUE) %>%
  mutate(Region = countrycode(Country, origin = "country.name", destination = "region")) %>%
  select(Country, Region) %>%
  drop_na()

only_south <- left_join(unigrams_corpus_1970on, northsouth_tbl) %>%
  filter(`Global South` == "Global South") %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  mutate(Year = cut_interval(Year, length = 5)) %>%
  group_by(Year) %>%
  count(word_stem) %>%
  group_by(Year) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(Year = as.factor(Year),
           name = reorder_within(word_stem, n, Year))

only_alignment <- left_join(unigrams_corpus_1970on, nonaligned_tbl) %>%
  anti_join(UN_stop_words, by = c("word_stem" = "words")) %>%
  mutate(Year = cut_interval(Year, length = 5)) %>%
  group_by(Year) %>%
  count(word_stem) %>%
  group_by(Year) %>%
  top_n(n = 10) %>%
  mutate(percent = n/sum(n)) %>%
  arrange(desc(n), .by_group = TRUE) %>%
  ungroup() %>%
  mutate(Year = as.factor(Year),
           name = reorder_within(word_stem, n, Year))


ggplot(data = only_south, mapping = aes(x = name, y = percent, fill = Year)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~Year, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Count (Percent of All Relevant Words Said During Period)",
         x = NULL,
         title = "Most Common Words Over Time (Global South States + Singapore)") +
    theme(title = element_text(size = 14), strip.text.x = element_text(face = "bold"), axis.text.y = element_text(size = 12))

ggplot(data = only_alignment, mapping = aes(x = name, y = percent, fill = Year)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~Year, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Count (Percent of All Relevant Words Said During Period)",
         x = NULL,
         title = "Most Common Words Over Time (Non Aligned States)") +
    theme(title = element_text(size = 14), strip.text.x = element_text(face = "bold"), axis.text.y = element_text(size = 12))
```

# Sentiment Analysis

This is for a later time and wasn't the focus of this project update. I'm keeping this here just so I have it in my backpocket for when it does become important later on in the project. 

```{r}
# corpus_affin df only contains words that have affinities mapped to them
unigrams_corpus_affin <- unigrams_corpus_1970on %>% 
  inner_join(get_sentiments("afinn"), by = c("word_stem" = "word"))

bigrams_corpus_affin <- bigrams_corpus_1970on %>% 
  inner_join(get_sentiments("afinn"), by = c("first_word_stem" = "word")) %>%
  inner_join(get_sentiments("afinn"), by = c("second_word_stem" = "word")) %>%
  mutate(mean_sentiment = (value.x+value.y)/2)
```
