---
title: "Mapping the Politics of the New Global South"
author: "Neeraj Sharma"
date: "7/31/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Introduction

I am working for Professor Mark Bradley in the History Department at the University of Chicago this summer on his research project, Mapping the Politics of the New Global South. 

# Setup

Prior to performing analysis on the data collected, it is necessary to prep the work environment so it contains all the packages necessary for exploration. 

## Load Packages

```{r}
# Relevant to data importation, structuring and visualization
library(tidyverse)
library(knitr)
library(readr)
library(here)

# Relevant to data formatting
library(lubridate)
library(countrycode)

# Relevant to text analysis
library(tidytext)
library(stringr)
library(SnowballC)
```

## Import datasets

These datasets were produced through the corpus_maker.R script. The original source files are from Mikhaylov.

```{r}
unigrams_corpus_1970on <- read_tsv(here::here("Data", "unigrams_mikhaylov_project.tsv")) %>%
  select(Session, Year, Country, word_stem)

bigrams_corpus_1970on <- read_tsv(here::here("Data", "bigrams_mikhaylov_project.tsv")) %>%
  select(Session, Year, Country, word_stem)
```

## Glimpse at the content of the datasets

Unigrams

```{r}
kable(unigrams_corpus_1970on %>% slice(1:10))
```

Bigrams

```{r}
kable(bigrams_corpus_1970on %>% filter(Session == 25) %>% slice(1:10))
```

# Analysis
